Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-11-17 prop_letter.tex
prop_letter.tex After meeting with Prof. Hanson individually...

\author{Andrew J Hanson}
\affiliation{Department of Informatics, Indiana University, Bloomington,
Indiana 47405, USA}

@@

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule determining the probability of a given
measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.  Here,
Gleason's theorem establishes that there is no alternative to the Born
rule by demonstrating, using reasonable continuity arguments in
Hilbert spaces of dimension $d\ge3$, the existence of a unique state
$\rho$ consistent with the statistical predictions computed from that
rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  Our
question then concerns what happens when infinite precision cannot be
achieved.  We are able to show that, while a QIVPM incorporating the
effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert space
$\Hilb$ of dimension $d\ge3$, there is a mathematically precise sense
in which one recovers the original Gleason theorem asymptotically.
Specifically, it is possible to construct a class of QIVPMs
representing bounded resources that is parameterized by the size of
the probability intervals of uncertainty. We then demonstrate that all
QIVPMs in this class are consistent with a non-empty set of quantum
states, and as the size of the intervals characterizing the
uncertainties goes to zero, this set of quantum states converges to
the unique state consistent with the Born rule. We furthermore
establish a mathematical correlation between the sizes of the
intervals and the volume of states that are all consistent with an
imprecise measurement.

The paper is organized as follows.  In Sec.~\ref{sec:fuzzy} we begin
by introducing the foundations of quantum probability space and fuzzy
measurement.  We then move on to introduce the concept of quantum
interval-valued probability in Sec.~\ref{sec:Interval-Uncertainty}.
The QIVPMs will provide the mathematical framework we need to quantify
the impact of finite precision measurements on quantum mechanics.  For
instance, in Sec.~\ref{sec:Kochen-Specker}, we quantify the domain of
validity of a contextual measurement, thus addressing the conditions
under which the Kochen-Specker theorem applies.  This provides a way
of not only resolving the Meyer-Mermin debate, but also revealing of a
precise transition to non-contextuality; these are the results of our
Thm.~\ref{cor:Kochen-Specker-IVPM}.  In Sec.~\ref{sec:Gleason}, we
study Gleason's theorem in the context of imprecise measurements,
concluding that QIVPMs provide a framework with quantitative bounds in
which Gleason's theorem, while formally invalid in a universe with
bounded resources, holds asymptotically in a mathematically precise
way.  Finally, we present our conclusions in
Sec.~\ref{sec:Conclusion}.

@@

First, for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability of impossible events (e.g., the null event)
and events that are certain (e.g., the event covering the entire
sample space).  For each interval $[\ell,r]$, we also need the dual
interval $[1-r,1-\ell]$ so that if one interval refers to the
probability of an event~$E$, the dual refers to the probability of the
event's complement $\overline{E}$.  For example, if we discover as a
result of an experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$,
we may conclude that $\mu(\overline{E}) = [0.7,0.8]$ for the
complementary event~$\overline{E}$. In addition to these simple
conditions, there are some subtle conditions on how intervals are
combined, which we discuss next.

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that
\emph{either} $E_1$ or $E_2$ occurs might be
$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
are disjoint; the naïve addition of intervals would give
$\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid probability
interval. Moreover the event $E\cup\overline{E}$ is the
entire space; its probability interval should be
$\necess$ which is sharper than $[0.9,1.1]$. The problem is that the
two intervals are correlated: there is more information in the
combined event than in each event separately. In our example, even
though the ``true'' probability of $E$ can be anywhere in the range
$[0.2,0.3]$ and the ``true'' probability of~$\overline{E}$ can be in
anywhere in the range $[0.7,0.8]$, the values are not independent. Any
value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
0.75$. To account for such subtleties, the axioms of interval-valued
probability do not use a strict equality for the combination of
disjoint events. The correct constraint regarding the probability of
$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is:
\begin{equation}
\label{eq:disjoint}
\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]
\end{equation}
which, in combination with the requirement for the event of the entire
space would force $\mu(E \cup \overline{E})$ to always be $\necess$
irrespective of the particular assignments of $\mu(E)$
or~$\mu(\overline{E})$.
%% Parallel arguments
%% can be made interpreting $[\ell,r]$ as Gaussian width, but will be omitted as no
%% essential new information seems to be introduced.

When combining non-disjoint events, there is a further subtlety whose
resolution will give us the final general condition for IVPMs. For
general, not necessarily disjoint, events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as \emph{convexity}
\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci1999,MarinacciMontrucchio2005,Grabisch2016},
reduces to the previously motivated Eq.~(\ref{eq:disjoint}) when the
events are disjoint, i.e., when $\mu(E_1\cap E_2) = 0$.

@@

We conclude this section with a generalization of expectation values
of observables in the context of QIVPMs. In conventional quantum
mechanics the expectation value of an observable as defined in
Eq.~\eqref{eq:quantum-expectation} is a unique real number. The
generalization to QIVPMs implies that this expectation value will
itself become bounded by or, more generally distributed around, an interval.

@@

\noindent This definition puts no restrictions on the set of intervals
itself, only on which intervals are assigned to events. When
$\delta=0$, every event must be assigned a probability either in the
interval $\imposs$ or in $\necess$, i.e., every event is completely
determined with certainty. As $\delta$ gets larger, the QIVPM allows
for more indeterminate behavior. For example, $\bar{\mu}_{A}$ defined
in Table~\ref{tab:classical-IVPMs} is $0$-deterministic because
$\imposs\subseteq\left[0,0\right]$ and
$\necess\subseteq\left[1-0,1\right]$.  By interpreting the states
~$\proj{0}$ and $\proj{1}$ as the head and the tail of a coin,
$\bar{\mu}_{A}$ represents tossing a double-headed coin. When $\delta$
is increased to $\frac{1}{3}$, both $\bar{\mu}_{B}$ and
$\bar{\mu}_{C}$ become $\frac{1}{3}$-deterministic. In contrast,
$\bar{\mu}_{2}$ defined in
Eq.~(\ref{eq:classical-no-information-IVPM}) is still not
$\frac{1}{3}$-deterministic because
$\bar{\mu}_{2}(\proj{0})=\bar{\mu}_{2}(\proj{1})=\unknown$, but
neither $\unknown\subseteq\left[0,\frac{1}{3}\right]$ nor
$\unknown\subseteq\left[1-\frac{1}{3},1\right]$.  Finally, when
$\delta=1$, because every interval is a subset of $\unknown$, every
QIVPM is $1$-deterministic. In particular, the non-informative
QIVPM~$\bar{\mu}_{1}$ defined in Eq.~(\ref{eq:no-information-IVPM}) is
1-deterministic.
%% and the Born QIVPM~$\bar{\mu}_{3}$ defined in
%% Eq.~(\ref{eq:Born-QIVPM}) are both $1$-deterministic.

@@

We can now proceed with the main technical result of this section. We
first observe that the original Kochen-Specker theorem is a statement
regarding the non-existence of a $0$-deterministic QIVPM, and
generalize to $\delta$-deterministic QIVPMs.

@@

Our framework allows us to generalize the above theorem to state that
for small enough $\delta$, it is impossible to have
$\delta$-deterministic QIVPMs. We next prove a main result of this
paper which is a stronger statement of contextuality that includes the
effects of finite-precision.  Every QIVPM must map some events to
truly uncertain intervals, not just ``almost definite intervals.''

@@

The proof is by contradiction: Suppose there is a
$\delta$-deterministic
QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. We will use this
assumed QIVPM to construct the following 0-deterministic QIVPM
$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
  \imposs,\necess\right\}$:
\[
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
\end{cases}
\]
However, since we know that 0-deterministic QIVPMs do not exist, the
map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ does
not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$ is
indeed a 0-deterministic QIVPM by checking that for orthogonal
projectors~$P_{0}$ and $P_{1}$, we have that
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
implies
$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\citep{TaiThesis2018}. Indeed
when
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and
$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
implies
$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
When $\delta<\frac{1}{3}$, i.e., $2\delta<1-\delta$, it follows that
$\bar{\mu}\left(P_{0}+P_{1}\right)$ cannot be a subset of
$\left[1-\delta,1\right]$. Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
is a subset of either $\left[0,\delta\right]$ or
$\left[1-\delta,1\right]$ and the latter is excluded, then
$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
$\left[0,\delta\right]$, which implies
$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Thus the
theorem holds when $\delta<\frac{1}{3}$.

The bound $\delta < \frac{1}{3}$ is tight as it is possible to
construct $\frac{1}{3}$-deterministic QIVPMs. For example, take $d=3$,
and let $P$ be a projector onto an $n$-dimensional subspace of
$\Hilb$, where $n \leq 3$. It is straightforward to check that
$\bar{\mu}\left(P\right)=\left[\frac{n}{3},\frac{n}{3}\right]$ is a
valid $\frac{1}{3}$-deterministic QIVPM.

When $\delta \geq \frac{1}{3}$, i.e, when the uncertainty in
measurements becomes that large, it becomes possible to map every
observable to some (quite inaccurate) probability interval, and hence
invalidating the Kochen-Specker theorem.

@@

We have quantified one important aspect of uncertainty in quantum
mechanics---due to the imprecise nature of devices---which is a novel
addition to the theory of measurement. Indeed, as Heisenberg
emphasized in his famous microscope
example~\cite{Heisenberg1983apsrev4}, the conventional theory
of measurement states that it is impossible to precisely measure any
property of a system without disturbing it somewhat. Thus, there are
fundamental limits to what one can measure and these limits have traditionally 
been attributed to complementarity. Our imprecision represents an 
\emph{additional} source of indeterminacy to the inherent probabilistic nature
of quantum mechanics.

% The significance of this observation is that the uncertainty in the
% intervals is, in contrast to the classical case, \emph{a fundamental
%   part of quantum theory}. There are in fact two sources of
% uncertainty: one due to the finite measurement resources and one due
% to complementarity, which requires every quantum framework to be truly
% probabilistic.

@@

A conventional quantum probability measure can be easily constructed
from a state $\rho$ according to the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.  According
to Gleason's
theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}, this
state $\rho$ is also the unique state consistent with any possible
probability measure. In order to re-examine these results in our
framework, we first reformulate Gleason's theorem in QIVPMs using
infinitely precise
intervals~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$:

\begin{thm}[$\mathscr{I}_{\infty}$ Variant of the Gleason
  Theorem]\label{cor:Gleason's}In
  a Hilbert space $\Hilb$ of dimension $d\geq3$, given a
  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$, the state
  $\rho$ consistent with it on every projector,
  $\coreBorn\left(\bar{\mu},\events\right)$, is unique. \end{thm}

As the intervals in the image of a QIVPM become less and less sharp,
we expect more and more states to be consistent with it. Indeed, in
the limit, the intervals become \imposs, \necess, and \unknown,  and
every state is consistent with an assignment that states that its
projections are unknown. There is however a subtlety: as shown in the
theorem below, an arbitrary assignment of intervals to projectors
might be globally inconsistent.

@@

\begin{tabular}{cc}
\toprule 
\addlinespace
$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, 
$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
\midrule 
\addlinespace
All other projectors & $\unknown$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Next we will prove by contradiction that
$\coreBorn\left(\bar{\mu},\events\right)$ is the empty set. Suppose
there is a state
$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j} > 0$. Since
$\muB_{\rho}(P)\in\bar{\mu}(P)$ for any~$P$, the
state~$\rho$ must satisfy:
\begin{equation}
\muB_{\rho}(\proj{0})=\muB_{\rho}(\proj{\ps})=\muB_{\rho}(\proj{\ps'})=0\,,
\end{equation}
which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all~$j$. The last equation never holds proving the theorem.

The fact that a collection of poor measurements on a quantum system
cannot reveal the underlying state is not surprising. Under certain
conditions, we can however guarantee that the uncertainty in
measurements is consistent with \emph{some} non-empty collection of
quantum states. Furthermore, we can relate the uncertainty in
measurements to the volume of quantum states such that, in the limit
of infinitely precise measurements, the volume of states collapses to
a single point corresponding to a single state.

To that end, we construct a family of QIVPMs parameterized by
\emph{blurring} functions $f:\left[0,1\right]\rightarrow\mathscr{I}$ that
formalize how the real-valued probabilities are mapped to
intervals. We also introduce a notion of norm that quantifies the
distance between (pure or mixed) states.  The norm of a pure
state $\rho=\proj{\psi}$ is defined as usual
$\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.  Similarly,
given any Hermitian operator~$A$, we consider the usual operator norm
$\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert
  =1}\left\Vert A\ket{\psi}\right\Vert $, which is also known as the
$2$-norm or the spectral
norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
Then, a finite-precision extension of Gleason's theorem can be stated as
follows.

>>>>

\author{Andrew J. Hanson}
\affiliation{Department of Informatics, Indiana University, Bloomington,
Indiana 47405, USA}

@@

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule determining the probability of a given
measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.  Here,
Gleason's theorem establishes that there is no alternative to the Born
rule by demonstrating, using reasonable continuity arguments in
Hilbert spaces of dimension $d\ge3$, the existence of a unique state
$\rho$ consistent with the statistical predictions computed from the Born
rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  Our
question then concerns what happens when infinite precision cannot be
achieved.  We are able to show that, while a QIVPM incorporating the
effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert space
$\Hilb$ of dimension $d\ge3$, there is a mathematically precise sense
in which one recovers the original Gleason theorem asymptotically.
Specifically, it is possible to construct a class of QIVPMs
representing bounded resources that is parameterized by the size of
the intervals. We then demonstrate that all
QIVPMs in this class are consistent with a non-empty set of quantum
states, and as the size of the intervals characterizing the
uncertainties goes to zero, this set of quantum states converges to
the unique state consistent with the Born rule. We furthermore
establish a mathematical correlation between the sizes of the
intervals and the volume of states that are all consistent with an
imprecise measurement.
\yutsung{``volume of states" are not defined in the Gleason's section.}

The paper is organized as follows.  In Sec.~\ref{sec:fuzzy} we begin
by introducing the foundations of quantum probability space and fuzzy
measurement.  We then move on to introduce the concept of quantum
interval-valued probability in Sec.~\ref{sec:Interval-Uncertainty}.
The QIVPMs will provide the mathematical framework we need to quantify
the impact of finite precision measurements on quantum mechanics.  For
instance, in Sec.~\ref{sec:Kochen-Specker}, we quantify the domain of
validity of a contextual measurement, thus addressing the conditions
under which the Kochen-Specker theorem applies.  This provides a way
not only of resolving the Meyer-Mermin debate, but also of revealing a
precise transition to non-contextuality; these are the results of our
Thm.~\ref{cor:Kochen-Specker-IVPM}.  In Sec.~\ref{sec:Gleason}, we
study Gleason's theorem in the context of imprecise measurements,
concluding that QIVPMs provide a framework with quantitative bounds in
which Gleason's theorem, while formally invalid in a universe with
bounded resources, holds asymptotically in a mathematically precise
way.  Finally, we present our conclusions in
Sec.~\ref{sec:Conclusion}.

@@

First, for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability interval for impossible events
and events that are certain. We can write this, respectively, as
$\mu(\emptyset)=\imposs$ and $\mu(\Omega)=\necess$, where $\emptyset$ is
the null event and $\Omega$ is the event covering the entire
sample space.  For each interval $[\ell,r]$, we also need the dual
interval $[1-r,1-\ell]$ so that if one interval refers to the
probability of an event~$E$, the dual refers to the probability of the
event's complement $\overline{E}$.  For example, if we discover as a
result of an experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$,
we may conclude that $\mu(\overline{E}) = [0.7,0.8]$ for the
complementary event~$\overline{E}$. In addition to these simple
conditions, there are some subtle conditions on how intervals are
combined, which we discuss next.

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that
\emph{either} $E_1$ or $E_2$ occurs might be
$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
are disjoint; the naïve addition of intervals would give
$\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid probability
interval. Moreover the event $E\cup\overline{E}$ is the
entire space; its probability interval should be
$\necess$ which is sharper than $[0.9,1.1]$. The problem is that the
two intervals are correlated: there is more information in the
combined event than in each event separately. In our example, even
though the ``true'' probability of $E$ can be anywhere in the range
$[0.2,0.3]$ and the ``true'' probability of~$\overline{E}$ can be
anywhere in the range $[0.7,0.8]$, the values are not independent. Any
value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
0.75$. To account for such subtleties, the axioms of interval-valued
probability do not use a strict equality for the combination of
disjoint events. The correct constraint enforcing coherence of
the probability assignment for
$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is:
\begin{equation}
\label{eq:disjoint}
\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]\,,
\end{equation}
which, in combination with the requirement for the event of the entire
space, would force $\mu(E \cup \overline{E})$ to always be $\necess$
irrespective of the particular assignments of $\mu(E)$
or~$\mu(\overline{E})$.
%% Parallel arguments
%% can be made interpreting $[\ell,r]$ as Gaussian width, but will be omitted as no
%% essential new information seems to be introduced.
\yutsung{Need to be rewrite and make it more clear. Say with symbol and
equation is better.}

When combining non-disjoint events, there is a further subtlety whose
resolution will give us the final general condition for IVPMs. For
events $E_1$ and $E_2$, necessarily disjoint, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)\,,
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as \emph{convexity}
\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci1999,MarinacciMontrucchio2005,Grabisch2016},
reduces to the previously motivated Eq.~(\ref{eq:disjoint}) when the
events are disjoint, i.e., when $\mu(E_1\cap E_2) = 0$.

@@

We conclude this section with a generalization of expectation values
of observables in the context of QIVPMs. In conventional quantum
mechanics the expectation value of an observable as defined in
Eq.~\eqref{eq:quantum-expectation} is a unique real number. The
generalization to QIVPMs implies that this expectation value will
itself become bounded by or, more generally, distributed around, an interval.

@@

\noindent This definition puts no restrictions on the set of intervals
itself, only on which intervals are assigned to events. When
$\delta=0$, every event must be assigned a probability either in the
interval $\imposs$ or in $\necess$, i.e., every event is completely
determined with certainty. As $\delta$ gets larger, the QIVPM allows
for more indeterminate behavior. For example, $\bar{\mu}_{A}$ defined
in Table~\ref{tab:classical-IVPMs} is $0$-deterministic because
$\imposs\subseteq\left[0,0\right]$ and
$\necess\subseteq\left[1-0,1\right]$.  By interpreting the states
~$\proj{0}$ and $\proj{1}$ as the head and the tail of a coin,
$\bar{\mu}_{A}$ represents tossing a double-headed coin. When $\delta$
is increased to $\frac{1}{3}$, both $\bar{\mu}_{B}$ and
$\bar{\mu}_{C}$ become $\frac{1}{3}$-deterministic. In contrast,
$\bar{\mu}_{A}$ is still not
$\frac{1}{3}$-deterministic because
$\bar{\mu}_{A}(\proj{0})=\bar{\mu}_{A}(\proj{1})=\unknown=[0,1]$, but
both $\unknown\subseteq\left[0,\frac{1}{3}\right]$ and
$\unknown\subseteq\left[1-\frac{1}{3},1\right]$ are false.  Finally, when
$\delta=1$, because every interval is a subset of $\unknown$, every
QIVPM is $1$-deterministic. In particular, the non-informative
QIVPM~$\bar{\mu}_{A}$ is
1-deterministic.
%% and the Born QIVPM~$\bar{\mu}_{3}$ defined in
%% Eq.~(\ref{eq:Born-QIVPM}) are both $1$-deterministic.

@@

We can now proceed with the main technical result of this section. We
first observe that the original Kochen-Specker theorem is a statement
regarding the non-existence of a $0$-deterministic QIVPM, and
generalize to a corresponding statement about $\delta$-deterministic QIVPMs.

@@

Our framework allows us to generalize the above theorem to state that
for small enough $\delta$, it is impossible to have
$\delta$-deterministic QIVPMs. We next prove a main result of this
paper which is a stronger statement of contextuality that includes the
effects of finite-precision.  Every QIVPM must map some events to
truly uncertain intervals, not just ``almost definite intervals.'' 
\yutsung{contextuality is never defined.}

@@

The proof is by contradiction: Suppose there is a
$\delta$-deterministic
QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this
assumed QIVPM to construct the following 0-deterministic QIVPM
$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
  \imposs,\necess\right\}$:
\[
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
\end{cases}
\]
However, since we know that 0-deterministic QIVPMs do not exist, the
map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ does
not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$ is
indeed a 0-deterministic QIVPM by checking that for orthogonal
projectors~$P_{0}$ and $P_{1}$, we have that
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
implies
$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\citep{TaiThesis2018}. Indeed
when
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and
$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
implies
$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
When $\delta<\frac{1}{3}$, i.e., $2\delta<1-\delta$, it follows that
$\bar{\mu}\left(P_{0}+P_{1}\right)$ cannot be a subset of
$\left[1-\delta,1\right]$. Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
is a subset of either $\left[0,\delta\right]$ or
$\left[1-\delta,1\right]$ and the latter is excluded, then
$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
$\left[0,\delta\right]$, which implies
$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Thus the
theorem holds when $\delta<\frac{1}{3}$.

The bound $\delta < \frac{1}{3}$ is tight as it is possible to
construct $\frac{1}{3}$-deterministic QIVPMs. For example, take $d=3$,
and let $P$ be a projector onto an $n$-dimensional subspace of
$\Hilb$, where $n \leq 3$. It is straightforward to check that
$\bar{\mu}\left(P\right)=\left[\frac{n}{3},\frac{n}{3}\right]$ is a
valid $\frac{1}{3}$-deterministic QIVPM.
\yutsung{Redefine $\bar{\mu}$ to be more clear!}

When $\delta \geq \frac{1}{3}$, i.e, when the uncertainty in
measurements becomes that large, it becomes possible to map every
observable to some (quite inaccurate) probability interval, thus
invalidating the Kochen-Specker theorem.

@@

We have thus quantified one important aspect of uncertainty in quantum
mechanics---the effect of the imprecise nature of devices---which is a novel
addition to the theory of measurement. Indeed, as Heisenberg
emphasized in his famous microscope
example~\cite{Heisenberg1983apsrev4}, the conventional theory
of measurement states that it is impossible to precisely measure any
property of a system without disturbing it somewhat. Thus, there are
fundamental limits to what one can measure and these limits have traditionally 
been attributed to complementarity. Our imprecision represents an 
\emph{additional} source of indeterminacy beyond the inherent probabilistic nature
of quantum mechanics.
\yutsung{To Amr, the ``beyond'' is changed from ``to''. Andy wants to make sure
you are OK with it.}
% The significance of this observation is that the uncertainty in the
% intervals is, in contrast to the classical case, \emph{a fundamental
%   part of quantum theory}. There are in fact two sources of
% uncertainty: one due to the finite measurement resources and one due
% to complementarity, which requires every quantum framework to be truly
% probabilistic.

@@

A conventional quantum probability measure can be easily constructed
from a state $\rho$ according to the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.  According
to Gleason's
theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}, this
state $\rho$ is also the unique state consistent with any possible
probability measure. In order to re-examine these results in our
framework, we first reformulate Gleason's theorem in QIVPMs using
infinitely precise uncountable
intervals~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$:

\begin{thm}[$\mathscr{I}_{\infty}$ Variant of the Gleason
  Theorem]\label{cor:Gleason's}In
  a Hilbert space $\Hilb$ of dimension $d\geq3$, given a
  QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$, the state
  $\rho$ consistent with $\bar{\mu}$ on every projector
  is unique, i.e., there exists a
  unique state~$\rho$ such that
  $\coreBorn\left(\bar{\mu},\events\right)=\{\rho\}$.
  \end{thm}

Now let us consider relaxing $\mathscr{I}$
to a countable set of finite-width intervals.
As the intervals in the image of a QIVPM become less and less sharp,
we expect more and more states to be consistent with it. Indeed, in
the limit, the intervals become \imposs, \necess, and \unknown,  and
every state is consistent with an assignment that states that its
projections are unknown. There is however a subtlety: as shown in the
theorem below, it is possible for an arbitrary assignment of intervals to projectors
to be globally inconsistent.

@@

\begin{tabular}{cc}
\toprule 
\addlinespace
$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, 
$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
\midrule 
\addlinespace
All other projectors & $\unknown$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Next we will prove by contradiction that
$\coreBorn\left(\bar{\mu},\events\right)$ is the empty set. Suppose
there is a state
$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j} > 0$. Since
we assumed the core is non-empty $\muB_{\rho}(P)\in\bar{\mu}(P)$, then
$\bar{\mu}(\proj{0})=\imposs=[0,0]$ from Table~\ref{tab:non-Born-QIVPM} requires
$\muB_{\rho}(P)=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
Therefore, $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all~$j$. The last equation never holds, proving the theorem.

The fact that a collection of poor measurements on a quantum system
cannot reveal the underlying state is not surprising. Under certain
conditions, we can however guarantee that the uncertainty in
measurements is consistent with \emph{some} non-empty collection of
quantum states. Furthermore, we can relate the uncertainty in
measurements to the volume of quantum states such that, in the limit
of infinitely precise measurements, the volume of states collapses to
a single state.

To that end, we construct a family of QIVPMs parameterized by
\emph{blurring} functions $f:\left[0,1\right]\rightarrow\mathscr{I}$ that
formalize how the real-valued probabilities are mapped to
intervals. We also introduce a notion of norm that quantifies the
distance between (pure or mixed) states.  The norm of a pure
state $\rho=\proj{\psi}$ is defined as usual by
$\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$.  Similarly,
given any Hermitian operator~$A$, we consider the usual operator norm
$\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert
  =1}\left\Vert A\ket{\psi}\right\Vert $, which is also known as the
$2$-norm or the spectral
norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
Then, a finite-precision extension of Gleason's theorem can be stated as
follows.
